Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-11 CJM/letter to CJM.tex
*Now* I'm done. Probably

\begin{enumerate}
\item[(1)] We are extremely grateful for this observation. We had made a mistake. Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper.
\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review. Our main motivation for Section 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups. (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
\end{enumerate}

\begin{enumerate}
\item[(i)] Thank you for noticing this. We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$. To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients. 
\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field $k$. 
\item[(iii)] We fixed this typo.
\item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
\item[(v)] We replaced every instance of $S$ with $\Spec{R}$, which is what we meant by $S$, though we had neglected to say that.
\item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper. We have also given a precise citation to Yu's paper showing where the "recursive definition" can be found.
\item[(vii)] Fixed this typo.
\end{enumerate}

>>>>

\begin{enumerate}
\item[(1)] We are extremely grateful for this observation. We had made a mistake. Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper. \todo{Should we say more?}
\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review. Our main motivation for Section 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups. (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
\end{enumerate}

\begin{enumerate}
\item[(i)] Thank you for noticing this. We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$. To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients. 
\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field $k$. 
\item[(iii)] We fixed this typo.
\item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
\item[(v)] We replaced every instance of $S$ with $\Spec{R}$, which is what we meant by $S$, though we had neglected to say that.
\item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper. In fact, we have expanded this chart from 5 to 11 rows, to make the comparison with Yu's paper easier. We have also given a precise citation to Yu's paper showing where the "recursive construction" can be found, there.
\item[(vii)] Fixed this typo.
\end{enumerate}
